Monte Carlo comparisons \\ VBSCAN Cost Action

### 2017-06-27 Setup/report.tex
added recola NLO number in tab3

\begin{table}[h!]
    \begin{tabular}{c|c|c|c}
        Code  &  $\sigma[\rm{fb}]$  &  $\sigma(n_j=2)[\rm{fb}]$  &  $\sigma(n_j=3)[\rm{fb}]$\\
        \hline
        \hline
        {\sc POWHEG}  &  $1.334 \pm 0.0003$  &  $0.808 \pm  0.001$  &  $0.5260 \pm 0.0005$\\
        {\sc Recola}  &  \\
        {\sc VBFNLO}  &  $1.3531 \pm 0.0003$  &  $0.8264 \pm  0.0003$  &  $0.5267 \pm 0.0001$\\
        {\sc BONSAY}  &  $1.3366 \pm 0.0009$  &  $0.8199 \pm  0.0008$  &  $0.51663 \pm 0.00007$ \\
        {\sc MG5\_aMC}&  $1.318  \pm 0.003$  &  $0.781 \pm  0.004$  &  $0.5374 \pm 0.0016$\\
    \end{tabular}
    \caption{\label{tab:NLOrates} NLO rates within VBS cuts from the different codes.}
\end{table}

>>>>

\begin{table}[h!]
    \begin{tabular}{c|c|c|c}
        Code  &  $\sigma[\rm{fb}]$  &  $\sigma(n_j=2)[\rm{fb}]$  &  $\sigma(n_j=3)[\rm{fb}]$\\
        \hline
        \hline
        {\sc POWHEG}  &  $1.334 \pm 0.0003$  &  $0.808 \pm  0.001$  &  $0.5260 \pm 0.0005$\\
        {\sc Recola}  &  $1.197 \pm 0.003 $ \\
        {\sc VBFNLO}  &  $1.3531 \pm 0.0003$  &  $0.8264 \pm  0.0003$  &  $0.5267 \pm 0.0001$\\
        {\sc BONSAY}  &  $1.3366 \pm 0.0009$  &  $0.8199 \pm  0.0008$  &  $0.51663 \pm 0.00007$ \\
        {\sc MG5\_aMC}&  $1.318  \pm 0.003$  &  $0.781 \pm  0.004$  &  $0.5374 \pm 0.0016$\\
    \end{tabular}
    \caption{\label{tab:NLOrates} NLO rates within VBS cuts from the different codes.}
\end{table}
